---
title: "Summary from ClinicalTrials.gov"
author: Alexandra Bannach-Brown
date: 2019-05-23
output: html_document
---

```{r setup, message=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)
# install.packages("devtools")
library(devtools)
# install_github("sachsmc/rclinicaltrials")
library(rclinicaltrials)
```

## Introduction

This is document which shows the summary information from ClinicalTrials.gov <http://clinicaltrials.gov>. This document is built for the EQUATOR Network. 


## Number of Trials

The number of records in clinicaltrials.gov is: 

```{r all trials}
clinicaltrials_count(query = "ALL")
```


## Actively Recruiting Trials

The number of trials that are currently recruiting is: 
```{r active trials}
clinicaltrials_count(query = c("recr=Recruiting", "ALL"))
```


## Completed Trials

The number of trials that are marked as completed:
```{r completed trials}
clinicaltrials_count(query = c("recr=Completed", "ALL"))
```


## New Trials in 2018
The number of new trials posted in 2018 is: 
```{r new trials 2018}
clinicaltrials_count(query = c("rcv_s=01/01/2018", "rcv_e=12/31/2018"))
```


Please contact Alexandra Bannach-Brown <mailto:alexandra_bannachbrown@bond.edu.au> if you have any questions. 

