---
title: "Identifying Systematic Reviews from PubMed"
author: "Alexandra Bannach-Brown on behalf of the EQUATOR Network"
date: "28 May 2019"
output: html_document
---

## Introduction

This is document which shows the summary information from ClinicalTrials.gov <http://clinicaltrials.gov>. This document is built for the EQUATOR Network. 



### Install packages & Set-Up
First we install and load the packages that we need to get data from the PubMed API.
```{r setup, include=FALSE}
## install and load libraries
# install.packages("rentrez")
library(rentrez)

# set up
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```

## Systematic Reviews

Then we query PubMed via the API to find the number of records that are systematic reviews and have the 'human' MeSH heading attached. 
```{r human sys rev }
# human systematic reviews pubmed query
sys_rev_human_query <- "(systematic review[PTYP] AND human[MESH])"
sys_rev_human_search <- entrez_search(db = "pubmed", sys_rev_human_query, use_history = TRUE )
sys_rev_human_search$count
```



We can visualise the number of systematic reviews published in the past 10 years.
```{r}
sys_rev_year <- function(year, term){
  query <- paste(term, "AND(", year, "[PDAT])")
  entrez_search(db="pubmed", term = query, retmax=0)$count
}

year <- 2008:2018
papers <- sapply(year, sys_rev_year, term="(systematic review[PTYP] AND human[MESH])", USE.NAMES = FALSE)
## produce the plots
plot(year, papers, type='b', main="Increase in Systematic Reviews - Count per year 2008:2018")
```



Please contact Alexandra Bannach-Brown <mailto:alexandra_bannachbrown@bond.edu.au> if you have any questions. 
