---
title: "Identifying Trials Registerd on ClinicalTrials.gov"
author: "Alexandra Bannach-Brown on behalf of the EQUATOR Network"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

## Introduction

This is a document which shows the summary information about trials registered in <a href="http://clinicaltrials.gov" target="_blank"> ClinicalTrials.gov </a>. 



```{r setup, include=FALSE}
## install packages
# install.packages("devtools")
# library(devtools)
# install_github("sachsmc/rclinicaltrials")

# load packages

library(rclinicaltrials)
library(knitr)
library(plotly)

# set-up
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```



## Total Number of Trials

The number of records in clinicaltrials.gov is: 
```{r all trials}
clinicaltrials_count(query = "ALL")
```


## Total Number of Actively Recruiting Trials

The number of trials that are currently recruiting is: 
```{r active trials}
clinicaltrials_count(query = c("recr=Recruiting", "ALL"))
```


## Total Number of Completed Trials

The number of trials that are marked as completed:
```{r completed trials}
clinicaltrials_count(query = c("recr=Completed", "ALL"))
```


## New Trials in 2018
The number of new trials posted in 2018 is: 
```{r new trials 2018}
clinicaltrials_count(query = c("rcv_s=01/01/2018", "rcv_e=12/31/2018"))
```


## New Trials in 2019
The number of new trials posted in 2019 is: 
```{r new trials 2019}
clinicaltrials_count(query = c("rcv_s=01/01/2019", "rcv_e=12/31/2019"))
```


## Trials Registered in the Past 10 years
Graph showing the increase in clinical intervention trials published in the last 10 years:
```{r over time}
#### code adapted from Billy Caughey tutorial 9th March 2017 https://rpubs.com/wgcaughey1984/257099 ##

##### Initial Values #####
startYear <- 2009
endYear <- 2019
##### Trials over time #####
months <- 1:12
years <- startYear:endYear
numOfTrials <- NULL
totalTrials <- NULL
startDate <- NULL

for(j in 1:length(years)){
  for(i in 1:length(months)){
    
    x <- clinicaltrials_count(query = c("type=Intr", 
                                        #"term=workplace+program OR workplace+wellness OR workplace+health+program", 
                                        paste("rcv_e=",months[i],"/01/",years[j],sep="")))
    numOfTrials <- c(numOfTrials,x)
    totalTrials <- c(totalTrials,sum(numOfTrials))
    startDate <- c(startDate,paste(months[i],"/01/",years[j],sep=""))
  }
}

## Put fields together
ctOverTime <- data.frame(startDate,numOfTrials)

## Convert start date to a date field
ctOverTime$startDate <- as.character(ctOverTime$startDate)
charLength <- nchar(ctOverTime$startDate) == 9
# cbind(ctOverTime$startDate,nchar(ctOverTime$startDate),charLength)
ctOverTime$startDate <- ifelse(charLength == TRUE,paste("0",ctOverTime$startDate,sep=""),
                               ctOverTime$startDate)
#### plot
ctOverTime$startDate <- as.Date(ctOverTime$startDate,"%m/%d/%Y")
with(ctOverTime, 
     
 plot(numOfTrials ~ startDate, type = "l",main="Number of Intervention Trials Registered 2009-2019", ylim = c(0,250000), xlab = "Time",ylab="Trials")
)
     
  #    plot_ly( x=~startDate) %>%
  # add_trace(
  #       type = 'scatter', y=~numOfTrials, 
  #       name = "Number of Intervention Trials Registered 2009-2019", mode = 'lines+markers',
  #       line = list(color = 'rgb(79,78,84)', width = 2)
  #         ) %>%
  # layout(
  #   title =  "Number of Intervention Trials Registered 2009-2019",
  #   xaxis = list(title ="Year"),
  #   yaxis = list(title ="Articles", rangemode = "tozero")
  # )
  #    
     

```



Please contact <a href="mailto:alexandra_bannachbrown@bond.edu.au" target="_blank"> Alexandra Bannach-Brown</a> if you have any questions. 

