---
title: "Identifying Systematic Review Protocols Registered on PROSPERO"
author: "Alexandra Bannach-Brown on behalf of the EQUATOR Network"
date: "23 August, 2019"
output: 
  html_document:
    code_folding: hide
---

## Introduction

This is a document which shows the summary information from <a href="https://www.crd.york.ac.uk/prospero/" target="_blank"> PROSPERO </a>about systematic review registrations. This document is built for the EQUATOR Network. 

```{r setup, include=FALSE}
## install and load libraries
# install.packages("plotly")
library(plotly)
library(tidyverse)

# set up
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```

## All Data 
Data from PROSPERO is kindly provided by Ruth Walker at PROSPERO. 

```{r}
# load csv files
prospero_all <- read.csv("~/Documents/auto_retrieval/prospero_numbers_all.csv", sep = ",", header=TRUE)

# plot
plot_ly(data = prospero_all, x=~Year) %>%
  add_trace(
        type = 'scatter', y=~Number_regos, 
        name = "Number of Registrations", mode = 'lines+markers',
        line = list(color = 'rgb(205, 12, 24)', width = 2)
        ) %>%
  layout(
    title =  "All systematic review registrations on PROSPERO",
    xaxis = list(title ="Year"),
    yaxis = list(title ="Registrations")
    )

```


## Clinical and General Registrations
```{r}
# load csv
prospero_clinical <- read.csv("~/Documents/auto_retrieval/prospero_numbers_clinical.csv", sep = ",", header = TRUE)
# plot
plot_ly(data = prospero_clinical, x=~Year) %>%
  add_trace(
        type = 'scatter', y=~Number_regos, 
        name = "Number of Registrations", mode = 'lines+markers',
        line = list(color = 'rgb(22, 96, 167)', width = 2)
        ) %>%
  layout(
    title =  "Clinical & General Systematic Review Registrations on PROSPERO",
    xaxis = list(title ="Year"),
    yaxis = list(title ="Registrations")
    )
```


# Animal Systematic Review Registrations
```{r}
# load csv
prospero_animal <- read.csv("~/Documents/auto_retrieval/prospero_numbers_animal.csv", sep = ",", header = TRUE)
# plot
plot_ly(data = prospero_animal, x=~Year) %>%
  add_trace(
        type = 'scatter', y=~Number_regos, 
        name = "Number of Registrations", mode = 'lines+markers',
        line = list(color = 'rgb(2, 2, 2)', width = 2)
        ) %>%
  layout(
    title =  "Animal Systematic Review Registrations on PROSPERO",
    xaxis = list(title ="Year"),
    yaxis = list(title ="Registrations")
    )


```


# Cochrane Systematic Review Registrations
```{r}
# load csv
prospero_cochrane <- read.csv("~/Documents/auto_retrieval/prospero_numbers_cochrane.csv", sep = ",", header = TRUE)
# plot
plot_ly(data = prospero_cochrane, x=~Year) %>%
  add_trace(
        type = 'scatter', y=~Number_regos, 
        name = "Number of Registrations", mode = 'lines+markers',
        line = list(color = 'rgb(147, 43, 140)', width = 2)
          ) %>%
  layout(
    title =  "Cochrane Systematic Review Registrations on PROSPERO",
    xaxis = list(title ="Year"),
    yaxis = list(title ="Registrations")
  )
```



Please contact <a href="mailto:alexandra_bannachbrown@bond.edu.au" target="_blank"> Alexandra Bannach-Brown</a> if you have any questions. 