---
title: "PROSPERO"
author: "Alexandra Bannach-Brown on behalf of the EQUATOR Network"
date: "23 August, 2019"
output: html_document
---

## Introduction

This is a document which shows the summary information from <a href="https://www.crd.york.ac.uk/prospero/" target="_blank"> PROSPERO </a>about systematic review registrations. This document is built for the EQUATOR Network. 

```{r setup, include=FALSE}
## install and load libraries
# set up
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```

## All Data 
Data from PROSPERO is kindly provided by Ruth Walker at PROSPERO. 

```{r}
# load csv files
prospero_all <- read.csv("~/Documents/auto_retrieval/prospero_numbers_all.csv", sep = ",", header=TRUE)
plot(prospero_all$Year, prospero_all$Number_regos, type='b', main = "All systematic review registrations on PROSPERO", xlab = "Year", ylab="Registrations")
```


## Clinical and General Registrations
```{r}
# load csv
prospero_clinical <- read.csv("~/Documents/auto_retrieval/prospero_numbers_clinical.csv", sep = ",", header = TRUE)
# plot
plot(prospero_clinical$Year, prospero_clinical$Number_regos, type='b', main = "Clinical & General Systematic Review Registrations on PROSPERO", xlab = "Year", ylab="Registrations")
```


## Animal Systematic Review Registrations
```{r}
# load csv
prospero_animal <- read.csv("~/Documents/auto_retrieval/prospero_numbers_animal.csv", sep = ",", header = TRUE)
# plot
plot(prospero_animal$Year, prospero_animal$Number_regos, type='b', main = "Animal Systematic Review Registrations on PROSPERO", xlab = "Year", ylab="Registrations")
```


## Cochrane Systematic Review Registrations
```{r}
# load csv
prospero_cochrane <- read.csv("~/Documents/auto_retrieval/prospero_numbers_cochrane.csv", sep = ",", header = TRUE)
# plot
plot(prospero_cochrane$Year, prospero_cochrane$Number_regos, type='b', main = "Cochrane Systematic Review Registrations on PROSPERO", xlab = "Year", ylab="Registrations")
```



Please contact <a href="mailto:alexandra_bannachbrown@bond.edu.au" target="_blank"> Alexandra Bannach-Brown</a> if you have any questions. 