---
title: "Identifying Systematic Reviews from PubMed"
author: "Alexandra Bannach-Brown on behalf of the EQUATOR Network"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    code_folding: hide
---

## Introduction

This is a document which shows the summary information from <a href="https://www.ncbi.nlm.nih.gov/pubmed" target="_blank"> PubMed</a> about the number of systematic reviews indexed. 


```{r setup, include=FALSE}
## install and load libraries
# install.packages("rentrez")
library(rentrez)
library(tidyverse)
library(plotly)

# set up
knitr::opts_chunk$set(echo = TRUE)
chooseCRANmirror(graphics=FALSE, ind=1)
```

## Systematic Reviews of Human Studies

We query PubMed via the API to find the number of records that are systematic reviews and have the 'human' MESH heading attached. 
```{r human sys rev human}
# human systematic reviews pubmed query
sys_rev_human_query <- "(systematic review[PTYP] AND human[MESH])"
sys_rev_human_search <- entrez_search(db = "pubmed", sys_rev_human_query, use_history = FALSE )
sys_rev_human_search$count
```


We can visualise the number of systematic reviews published in the past 10 years.
```{r sys rev human graph}
sys_rev_year <- function(year, term){
  query <- paste(term, "AND(", year, "[PDAT])")
  entrez_search(db="pubmed", term = query, retmax=0)$count
}

year <- 2008:2019
papers <- sapply(year, sys_rev_year, term="(systematic review[PTYP] AND human[MESH])", USE.NAMES = FALSE)
## produce the plots
# plot(year, papers, type='b', main="Increase in Human Systematic Reviews - Count per year 2008:2018", 
#       ylim =  c(0,17000),
#       xlab = "Year",
#       ylab="Articles")

plot_ly( x=~year) %>%
  add_trace(
        type = 'scatter', y=~papers, 
        name = "Number of Systematic Reviews Published", mode = 'lines+markers',
        line = list(color = 'rgb(171,39,79)', width = 2)
          ) %>%
  layout(
    title =  "Increase in Human Systematic Reviews - Count per year 2008:2019",
    xaxis = list(title ="Year"),
    yaxis = list(title ="Articles", rangemode = "tozero")
  )

```


## Systematic Reviews of Animal Studies
Then we query PubMed via the API to find the number of records that are systematic reviews and 'animal' MeSH heading. 
```{r sys rev animal}
alt_animal_query <- "(systematic review[PTYP] AND animal[MESH] NOT human[MESH])"

sys_rev_animal_search <- entrez_search(db = "pubmed", alt_animal_query, use_history = FALSE)
sys_rev_animal_search$count
```

We can visualise the number of animal systematic reviews published in the past 10 years.
```{r sys rev animal graph}
sys_rev_year <- function(year, term){
  query <- paste(term, "AND(", year, "[PDAT])")
  entrez_search(db="pubmed", term = query, retmax=0)$count
}

year <- 2008:2019
papers_animal <- sapply(year, sys_rev_year, term="(systematic review[PTYP] AND animal[MESH] NOT human[MESH])", USE.NAMES = FALSE)
## produce the plots
# plot(year, papers_animal, type='b', main="Increase in Animal Systematic Reviews - Count per year 2008:2018", 
#      ylim =  c(0,150),
#      xlab = "Year",
#      ylab="Articles")

plot_ly( x=~year) %>%
  add_trace(
        type = 'scatter', y=~papers_animal, 
        name = "Number of Systematic Reviews Published", mode = 'lines+markers',
        line = list(color = 'rgb(124,185,232)', width = 2)
          ) %>%
  layout(
    title =  "Increase in Animal Systematic Reviews - Count per year 2008:2019",
    xaxis = list(title ="Year"),
    yaxis = list(title ="Articles", rangemode = "tozero")
  )
```


Please contact <a href="mailto:alexandra_bannachbrown@bond.edu.au" target="_blank"> Alexandra Bannach-Brown</a> if you have any questions. 
